### 2020-01-18 paper/sex_selection_spacing-ver3.tex
Ignore 4th spell for highest and add tables

\begin{figure}[htpb]
\centering
\rotatebox[origin=c]{90}{\small{Urban}}
\subfloat[Second Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{bs_spell2_high_urban_all}
    \end{minipage}
} 
\subfloat[Third Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{bs_spell3_high_urban_all} 
    \end{minipage}
}
\subfloat[Fourth Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{bs_spell4_high_urban_all}
    \end{minipage}
}
\\
\rotatebox[origin=c]{90}{\small{Rural}}
\subfloat[Second Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{bs_spell2_high_rural_all}
    \end{minipage}
} 
\subfloat[Third Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{bs_spell3_high_rural_all} 
    \end{minipage}
} 
\subfloat[Fourth Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{bs_spell4_high_rural_all} 
    \end{minipage}
} 
\caption{Estimated average spell length, sex ratio, and probability of 
a next birth for women with eight or more years of education}
\label{fig:bootstrap_high}
\end{figure}

@@

\begin{figure}[htpb]
\centering
\rotatebox[origin=c]{90}{\small{Urban}}
\subfloat[Second Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{bs_spell2_highest_urban_all}
    \end{minipage}
} 
\subfloat[Third Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{bs_spell3_highest_urban_all} 
    \end{minipage}
}
\subfloat[Fourth Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{bs_spell4_highest_urban_all}
    \end{minipage}
}
\\
\rotatebox[origin=c]{90}{\small{Rural}}
\subfloat[Second Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{bs_spell2_highest_rural_all}
    \end{minipage}
} 
\subfloat[Third Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{bs_spell3_highest_rural_all} 
    \end{minipage}
} 
\subfloat[Fourth Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{bs_spell4_highest_rural_all} 
    \end{minipage}
} 
\caption{Estimated average spell length, sex ratio, and probability of 
a next birth for women with eight or more years of education}
\label{fig:bootstrap_highest}
\end{figure}

@@

\section{Characteristics of Women Work Experiences}

@@

@@

>>>>

\begin{figure}[htpb]
\centering
\rotatebox[origin=c]{90}{\small{Urban}}
\subfloat[Second Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{bs_spell2_high_urban_all}
    \end{minipage}
} 
\subfloat[Third Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{bs_spell3_high_urban_all} 
    \end{minipage}
}
\subfloat[Fourth Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{bs_spell4_high_urban_all}
    \end{minipage}
}
\\
\rotatebox[origin=c]{90}{\small{Rural}}
\subfloat[Second Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{bs_spell2_high_rural_all}
    \end{minipage}
} 
\subfloat[Third Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{bs_spell3_high_rural_all} 
    \end{minipage}
} 
\subfloat[Fourth Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{bs_spell4_high_rural_all} 
    \end{minipage}
} 
\caption{Estimated average spell length, sex ratio, and probability of 
a next birth for women with eight to eleven years of education}
\label{fig:bootstrap_high}
\end{figure}

@@

\begin{figure}[htpb]
\centering
\rotatebox[origin=c]{90}{\small{Urban}}
\subfloat[Second Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{bs_spell2_highest_urban_all}
    \end{minipage}
} 
\subfloat[Third Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{bs_spell3_highest_urban_all} 
    \end{minipage}
}
\\
\rotatebox[origin=c]{90}{\small{Rural}}
\subfloat[Second Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{bs_spell2_highest_rural_all}
    \end{minipage}
} 
\subfloat[Third Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{bs_spell3_highest_rural_all} 
    \end{minipage}
} 
\caption{Estimated average spell length, sex ratio, and probability of 
a next birth for women with twelve or more years of education}
\label{fig:bootstrap_highest}
\end{figure}

@@

\section{Characteristics of Women's Work Experiences}

@@

\input{../tables/bootstrap_duration_avg_sex_ratio_highest_all.tex}

@@

\input{../tables/bootstrap_duration_p25_p75_highest_all.tex}
